
\chapter{Conclusion}
\vspace{0.5cm}

This work presents a comprehensive multimodal financial forecasting system that integrates time series analysis, sentiment extraction, and advanced machine learning for robust market prediction. By fusing features from Prophet, VADER, rolling statistics, and XGBoost, the system demonstrates significant improvements in predictive accuracy and resilience to market anomalies.

\section{Critical Reflection}
The modular design allows for flexible integration of new data sources and algorithms. Extensive benchmarking against traditional models highlights the superiority of the fusion approach, especially during periods of high volatility. However, the system's performance is still sensitive to extreme market events and data quality issues.

\section{Limitations}
\begin{itemize}
	\item \textbf{Data Dependency:} The accuracy depends on the availability and reliability of both financial and sentiment data.
	\item \textbf{Model Complexity:} Fusion models require careful tuning and may be computationally intensive for real-time deployment.
	\item \textbf{Generalizability:} Results may vary across different markets and asset classes; further validation is needed.
\end{itemize}

\section{Recommendations and Future Scope}
Future work should focus on:
\begin{itemize}
	\item Integrating alternative data sources (e.g., social media, macroeconomic indicators, alternative financial signals)
	\item Exploring deep learning architectures for feature extraction and fusion
	\item Real-time deployment and continuous learning to adapt to evolving market conditions
	\item Enhancing interpretability and explainability for decision support
\end{itemize}

Continuous benchmarking and adaptation will ensure the system remains relevant and effective in dynamic financial environments.